Portfolio conservation of metapopulations\\under climate change

### 2013-12-13 inst/ms/salmonfolios.tex
Clean main .tex file, fix numbers, declare file extension

\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}
\textheight 20.5cm
%\topmargin -1.43cm
%\oddsidemargin 1.2cm
%\evensidemargin 1.2cm
%\textwidth 14.5cm
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\usepackage{booktabs}

@@

%\usepackage{fontspec}
%\defaultfontfeatures{Ligatures=TeX}
%\setsansfont{Calibri}
%\setmonofont{Inconsolata}
%\usepackage{mathptmx}
%\setmainfont{Minion Pro}

@@

\bibitem[{Cooper \& Mangel(1999)}]{cooper1999}
7.\\
Cooper, A.~B. \& Mangel, M. (1999).
\newblock The dangers of ignoring metapopulation structure for the conservation
  of salmonids.
\newblock \emph{Fish. Bull.}, 97, 213--226.

\bibitem[{Crozier \emph{et~al.}(2008)Crozier, Hendry, Lawson, Quinn, Mantua,
  Battin, Shaw \& Huey}]{crozier2008}
8.\\
Crozier, L.~G., Hendry, A.~P., Lawson, P.~W., Quinn, T., Mantua, N.~J., Battin,
  J., Shaw, R.~G. \& Huey, R.~B. (2008).
\newblock Potential responses to climate change in organisms with complex life
  histories: evolution and plasticity in {Pacific} salmon.
\newblock \emph{Evol. Appl.}, 1, 252--270.

\bibitem[{de~Mazancourt \emph{et~al.}(2013)de~Mazancourt, Isbell, Larocque,
  Berendse, De~Luca, Grace, Haegeman, Wayne~Polley, Roscher, Schmid, Tilman,
  van Ruijven, Weigelt, Wilsey \& Loreau}]{demazancourt2013}
9.\\
de~Mazancourt, C., Isbell, F., Larocque, A., Berendse, F., De~Luca, E., Grace,
  J.~B., Haegeman, B., Wayne~Polley, H., Roscher, C., Schmid, B., Tilman, D.,
  van Ruijven, J., Weigelt, A., Wilsey, B.~J. \& Loreau, M. (2013).
\newblock Predicting ecosystem stability from community composition and
  biodiversity.
\newblock \emph{Ecol. Lett.}, 16, 617--625.

\bibitem[{DFO(2005)}]{dfo2005wsp}
10.\\
DFO (2005).
\newblock Canada's policy for conservation of wild {Pacific} salmon.
\newblock Tech. rep., Fisheries and Oceans Canada, Vancouver, BC.

\bibitem[{Eliason \emph{et~al.}(2011)Eliason, Clark, Hague, Hanson, Gallagher,
  Jeffries, Gale, Patterson, Hinch \& Farrell}]{eliason2011}
11.\\
Eliason, E.~J., Clark, T.~D., Hague, M.~J., Hanson, L.~M., Gallagher, Z.~S.,
  Jeffries, K.~M., Gale, M.~K., Patterson, D.~A., Hinch, S.~G. \& Farrell,
  A.~P. (2011).
\newblock Differences in thermal tolerance among sockeye salmon populations.
\newblock \emph{Science}, 332, 109--112.

\bibitem[{Elmqvist \emph{et~al.}(2003)Elmqvist, Folke, Nystr{\"o}m, Peterson,
  Bengtsson, Walker \& Norberg}]{elmqvist2003}
12.\\
Elmqvist, T., Folke, C., Nystr{\"o}m, M., Peterson, G., Bengtsson, J., Walker,
  B. \& Norberg, J. (2003).
\newblock Response diversity, ecosystem change, and resilience.
\newblock \emph{Front. Ecol. Environ.}, 1, 488--494.

\bibitem[{Figge(2004)}]{figge2004}
13.\\
Figge, F. (2004).
\newblock Bio-folio: applying portfolio theory to biodiversity.
\newblock \emph{Biodivers. Conserv.}, 13, 827--849.

\bibitem[{Fraser \emph{et~al.}(2011)Fraser, Weir, Bernatchez, Hansen \&
  Taylor}]{fraser2011}
14.\\
Fraser, D.~J., Weir, L.~K., Bernatchez, L., Hansen, M.~M. \& Taylor, E.~B.
  (2011).
\newblock Extent and scale of local adaptation in salmonid fishes: review and
  meta-analysis.
\newblock \emph{Heredity}, 106, 404--420.

\bibitem[{Gustafson \emph{et~al.}(2007)Gustafson, Waples, Myers, Weitkamp,
  Bryant, Johnson \& Hard}]{gustafson2007}
15.\\
Gustafson, R.~G., Waples, R.~S., Myers, J.~M., Weitkamp, L.~A., Bryant, G.~J.,
  Johnson, O.~W. \& Hard, J.~J. (2007).
\newblock Pacific salmon extinctions: quantifying lost and remaining diversity.
\newblock \emph{Conserv. Biol.}, 21, 1009--1020.

\bibitem[{Haak \& Williams(2012)}]{haak2012}
16.\\
Haak, A.~L. \& Williams, J.~E. (2012).
\newblock Spreading the risk: native trout management in a warmer and
  less-certain future.
\newblock \emph{N. Am. J. Fish. Manage.}, 32, 387--401.

\bibitem[{Hannah \emph{et~al.}(2002)Hannah, Midgley, Lovejoy, Bond, Bush,
  Lovett, Scott \& Woodward}]{hannah2002a}
17.\\
Hannah, L., Midgley, G.~F., Lovejoy, T., Bond, W.~J., Bush, M., Lovett, J.~C.,
  Scott, D. \& Woodward, F.~I. (2002).
\newblock Conservation of biodiversity in a changing climate.
\newblock \emph{Conserv. Biol.}, 16, 264--268.

\bibitem[{Hilborn \emph{et~al.}(2003)Hilborn, Quinn, Schindler \&
  Rogers}]{hilborn2003}
18.\\
Hilborn, R.~W., Quinn, T., Schindler, D. \& Rogers, D. (2003).
\newblock Biocomplexity and fisheries sustainability.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 100, 6564--6568.

\bibitem[{Hilborn \& Walters(1992)}]{hilborn1992}
19.\\
Hilborn, R.~W. \& Walters, C. (1992).
\newblock \emph{Quantitative Fisheries Stock Assessment: Choice, Dynamics, and
  Uncertainty}.
\newblock Chapman and Hall, London.

\bibitem[{Ives \& Carpenter(2007)}]{ives2007}
20.\\
Ives, A.~R. \& Carpenter, S.~R. (2007).
\newblock Stability and diversity of ecosystems.
\newblock \emph{Science}, 317, 58--62.

\bibitem[{Johnson \& Schindler(2013)}]{johnson2013a}
21.\\
Johnson, S.~P. \& Schindler, D.~E. (2013).
\newblock Marine trophic diversity in an anadromous fish is linked to its
  life-history variation in fresh water.
\newblock \emph{Biol. Lett.}, 9, 20120824.

\bibitem[{Koellner \& Schmitz(2006)}]{koellner2006}
22.\\
Koellner, T. \& Schmitz, O.~J. (2006).
\newblock Biodiversity, ecosystem function, and investment risk.
\newblock \emph{BioScience}, 56, 977--985.

\bibitem[{Lackey(2003)}]{lackey2003}
23.\\
Lackey, R.~T. (2003).
\newblock {Pacific Northwest} salmon: Forecasting their status in 2100.
\newblock \emph{Rev. Fish. Sci.}, 11, 35--88.

\bibitem[{Margules \& Pressey(2000)}]{margules2000}
24.\\
Margules, C.~R. \& Pressey, R.~L. (2000).
\newblock Systematic conservation planning.
\newblock \emph{Nature}, 405, 243--253.

\bibitem[{Markowitz(1952)}]{markowitz1952}
25.\\
Markowitz, H. (1952).
\newblock Portfolio selection.
\newblock \emph{J. Finance}, 7, 77--91.

\bibitem[{McClure \emph{et~al.}(2008{\natexlab{a}})McClure, Carlson, Beechie,
  Pess, Jorgensen, Sogard, Sultan, Holzer, Travis, Sanderson, Power \&
  Carmichael}]{mcclure2008a}
26.\\
McClure, M.~M., Carlson, S.~M., Beechie, T.~J., Pess, G.~R., Jorgensen, J.~C.,
  Sogard, S.~M., Sultan, S.~E., Holzer, D.~M., Travis, J., Sanderson, B.~L.,
  Power, M.~E. \& Carmichael, R.~W. (2008{\natexlab{a}}).
\newblock Evolutionary consequences of habitat loss for {Pacific} anadromous
  salmonids.
\newblock \emph{Evol. Appl.}, 1, 300--318.

\bibitem[{McClure \emph{et~al.}(2008{\natexlab{b}})McClure, Utter, Baldwin,
  Carmichael, Hassemer, Howell, Spruell, Cooney, Schaller \&
  Petrosky}]{mcclure2008b}
27.\\
McClure, M.~M., Utter, F.~M., Baldwin, C., Carmichael, R.~W., Hassemer, P.~F.,
  Howell, P.~J., Spruell, P., Cooney, T.~D., Schaller, H.~A. \& Petrosky, C.~E.
  (2008{\natexlab{b}}).
\newblock Evolutionary effects of alternative artificial propagation programs:
  implications for viability of endangered anadromous salmonids.
\newblock \emph{Evol. Appl.}, 1, 356--375.

\bibitem[{McCullough(1999)}]{mccullough1999}
28.\\
McCullough, D.~A. (1999).
\newblock A review and synthesis of effects of alterations to the water
  temperature regime on freshwater life stages of salmonids, with special
  reference to {Chinook} salmon.
\newblock EPA 910-R-99-010, US Environmental Protection Agency.

\bibitem[{McElhany \emph{et~al.}(2000)McElhany, Ruckelshaus, Ford, Wainwright
  \& Bjorkstedt}]{mcelhany2000}
29.\\
McElhany, P., Ruckelshaus, M.~H., Ford, M.~J., Wainwright, T.~C. \& Bjorkstedt,
  E.~P. (2000).
\newblock {Viable Salmonid Populations} and the recovery of {Evolutionarily
  Significant Units}.
\newblock Tech. Rep. NOAA Tech. Memo. NMFS-NWFSC-42, U.S. Deptartment of
  Commerce.

\bibitem[{Moore \emph{et~al.}(2010)Moore, Mcclure, Rogers \&
  Schindler}]{moore2010}
30.\\
Moore, J.~W., Mcclure, M., Rogers, L.~A. \& Schindler, D.~E. (2010).
\newblock Synchronization and portfolio performance of threatened salmon.
\newblock \emph{Conserv. Lett.}, 3, 340--348.

\bibitem[{Mori \emph{et~al.}(2013)Mori, Furukawa \& Sasaki}]{mori2013}
31.\\
Mori, A.~S., Furukawa, T. \& Sasaki, T. (2013).
\newblock Response diversity determines the resilience of ecosystems to
  environmental change.
\newblock \emph{Biol. Rev.}, 88, 349--364.

\bibitem[{Patterson \emph{et~al.}(2007)Patterson, Skibo, Barnes, Hills \&
  Macdonald}]{patterson2007}
32.\\
Patterson, D.~A., Skibo, K.~M., Barnes, D.~P., Hills, J.~A. \& Macdonald, J.~S.
  (2007).
\newblock The influence of water temperature on time to surface for adult
  sockeye salmon carcasses and the limitations in estimating salmon carcasses
  in the {Fraser River, British Columbia}.
\newblock \emph{N. Am. J. Fish. Manage.}, 27, 878--884.

\bibitem[{Pressey \emph{et~al.}(2007)Pressey, Cabeza, Watts, Cowling \&
  Wilson}]{pressey2007}
33.\\
Pressey, R.~L., Cabeza, M., Watts, M.~E., Cowling, R.~M. \& Wilson, K.~A.
  (2007).
\newblock Conservation planning in a changing world.
\newblock \emph{Trends Ecol. Evolut.}, 22, 583--592.

\bibitem[{Quinn(2005)}]{quinn2005}
34.\\
Quinn, T.~P. (2005).
\newblock \emph{The Behaviour and Ecology of Pacific Salmon and Trout}.
\newblock American Fisheries Society, Bethesda, Maryland.

\bibitem[{{\texttt{R} Core Team}(2013)}]{r2013}
35.\\
{\texttt{R} Core Team} (2013).
\newblock \emph{\texttt{R}: {A} language and environment for statistical
  computing}.
\newblock \texttt{R} Foundation for Statistical Computing, Vienna, Austria.

\bibitem[{Rogers \& Schindler(2008)}]{rogers2008}
36.\\
Rogers, L.~A. \& Schindler, D.~E. (2008).
\newblock Asynchrony in population dynamics of sockeye salmon in southwest
  {Alaska}.
\newblock \emph{Oikos}, 117, 1578--1586.

\bibitem[{Ruckelshaus \emph{et~al.}(2002)Ruckelshaus, Levin, Johnson \&
  Kareiva}]{ruckelshaus2002}
37.\\
Ruckelshaus, M.~H., Levin, P., Johnson, J.~B. \& Kareiva, P.~M. (2002).
\newblock The {Pacific} salmon wars: what science brings to the challenge of
  recovering species.
\newblock \emph{Annu. Rev. Ecol. Syst.}, 33, 665--706.

\bibitem[{Scheuerell \emph{et~al.}(2006)Scheuerell, Hilborn, Ruckelshaus,
  Bartz, Lagueux, Haas \& Rawson}]{scheuerell2006}
38.\\
Scheuerell, M.~D., Hilborn, R., Ruckelshaus, M.~H., Bartz, K.~K., Lagueux,
  K.~M., Haas, A.~D. \& Rawson, K. (2006).
\newblock The {Shiraz} model: a tool for incorporating anthropogenic effects
  and fish--habitat relationships in conservation planning.
\newblock \emph{Can. J. Fish. Aquat. Sci.}, 63, 1596--1607.

\bibitem[{Schindler \emph{et~al.}(2008)Schindler, Augerot, Fleishman, Mantua,
  Riddell, Ruckelshaus, Seeb \& Webster}]{schindler2008}
39.\\
Schindler, D.~E., Augerot, X., Fleishman, E., Mantua, N.~J., Riddell, B.,
  Ruckelshaus, M., Seeb, J. \& Webster, M. (2008).
\newblock Climate change, ecosystem impacts, and management for {Pacific}
  salmon.
\newblock \emph{Fisheries}, 33, 502--506.

\bibitem[{Schindler \emph{et~al.}(2010)Schindler, Hilborn, Chasco, Boatright,
  Quinn, Rogers \& Webster}]{schindler2010}
40.\\
Schindler, D.~E., Hilborn, R., Chasco, B., Boatright, C.~P., Quinn, T.~P.,
  Rogers, L.~A. \& Webster, M.~S. (2010).
\newblock Population diversity and the portfolio effect in an exploited
  species.
\newblock \emph{Nature}, 465, 609--612.

\bibitem[{Schtickzelle \& Quinn(2007)}]{schtickzelle2007}
41.\\
Schtickzelle, N. \& Quinn, T.~P. (2007).
\newblock A metapopulation perspective for salmon and other anadromous fish.
\newblock \emph{Fish Fish.}, 8, 297--314.

\bibitem[{Stockwell \emph{et~al.}(2003)Stockwell, Hendry \&
  Kinnison}]{stockwell2003}
42.\\
Stockwell, C., Hendry, A. \& Kinnison, M. (2003).
\newblock Contemporary evolution meets conservation biology.
\newblock \emph{Trends. Ecol. Evol.}, 18, 94--101.

\bibitem[{Thibaut \emph{et~al.}(2012)Thibaut, Connolly \&
  Sweatman}]{thibaut2012}
43.\\
Thibaut, L., Connolly, S.~R. \& Sweatman, H. P.~A. (2012).
\newblock Diversity and stability of herbivorous fishes on coral reefs.
\newblock \emph{Ecology}, 93, 891--901.

\bibitem[{Thomas(2010)}]{thomas2010}
44.\\
Thomas, C.~D. (2010).
\newblock Climate, climate change and range boundaries.
\newblock \emph{Divers. Distrib.}, 16, 488--495.

\bibitem[{Thomas \emph{et~al.}(2004)Thomas, Cameron, Green, Bakkenes, Beaumont,
  Collingham, Erasmus, de~Siqueira, Grainger, Hannah, Hughes, Huntley, van
  Jaarsveld, Midgley, Miles, Ortega-Huerta, Townsend~Peterson, Phillips \&
  Williams}]{thomas2004}
45.\\
Thomas, C.~D., Cameron, A., Green, R.~E., Bakkenes, M., Beaumont, L.~J.,
  Collingham, Y.~C., Erasmus, B. F.~N., de~Siqueira, M.~F., Grainger, A.,
  Hannah, L., Hughes, L., Huntley, B., van Jaarsveld, A.~S., Midgley, G.~F.,
  Miles, L., Ortega-Huerta, M.~A., Townsend~Peterson, A., Phillips, O.~L. \&
  Williams, S.~E. (2004).
\newblock Extinction risk from climate change.
\newblock \emph{Nature}, 427, 145--148.

\bibitem[{Thorson \emph{et~al.}(2013)Thorson, Scheuerell, Buhle \&
  Copeland}]{thorson2013}
46.\\
Thorson, J.~T., Scheuerell, M.~D., Buhle, E.~R. \& Copeland, T. (2013).
\newblock Spatial variation buffers temporal fluctuations in early juvenile
  survival for an endangered {Pacific} salmon.
\newblock \emph{J. Anim. Ecol.}, In press. doi:10.1111/1365-2656.12117.

\bibitem[{Vert-pre \emph{et~al.}(2013)Vert-pre, Amoroso, Jensen \&
  Hilborn}]{vert-pre2013}
47.\\
Vert-pre, K.~A., Amoroso, R.~O., Jensen, O.~P. \& Hilborn, R. (2013).
\newblock Frequency and intensity of productivity regime shifts in marine fish
  stocks.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 110, 1779--1784.

>>>>

\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}
\textheight 20.5cm
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\usepackage{booktabs}

\DeclareGraphicsExtensions{.eps}

@@

@@

\bibitem[{Carlson \& Satterthwaite(2011)}]{carlson2011}
7.\\
Carlson, S.~M. \& Satterthwaite, W.~H. (2011).
\newblock Weakened portfolio effect in a collapsed salmon population complex.
\newblock \emph{Can. J. Fish. Aquat. Sci.}, 68, 1579--1589.

\bibitem[{Cooper \& Mangel(1999)}]{cooper1999}
8.\\
Cooper, A.~B. \& Mangel, M. (1999).
\newblock The dangers of ignoring metapopulation structure for the conservation
  of salmonids.
\newblock \emph{Fish. Bull.}, 97, 213--226.

\bibitem[{Crozier \emph{et~al.}(2008)Crozier, Hendry, Lawson, Quinn, Mantua,
  Battin, Shaw \& Huey}]{crozier2008}
9.\\
Crozier, L.~G., Hendry, A.~P., Lawson, P.~W., Quinn, T., Mantua, N.~J., Battin,
  J., Shaw, R.~G. \& Huey, R.~B. (2008).
\newblock Potential responses to climate change in organisms with complex life
  histories: evolution and plasticity in {Pacific} salmon.
\newblock \emph{Evol. Appl.}, 1, 252--270.

\bibitem[{de~Mazancourt \emph{et~al.}(2013)de~Mazancourt, Isbell, Larocque,
  Berendse, De~Luca, Grace, Haegeman, Wayne~Polley, Roscher, Schmid, Tilman,
  van Ruijven, Weigelt, Wilsey \& Loreau}]{demazancourt2013}
10.\\
de~Mazancourt, C., Isbell, F., Larocque, A., Berendse, F., De~Luca, E., Grace,
  J.~B., Haegeman, B., Wayne~Polley, H., Roscher, C., Schmid, B., Tilman, D.,
  van Ruijven, J., Weigelt, A., Wilsey, B.~J. \& Loreau, M. (2013).
\newblock Predicting ecosystem stability from community composition and
  biodiversity.
\newblock \emph{Ecol. Lett.}, 16, 617--625.

\bibitem[{DFO(2005)}]{dfo2005wsp}
11.\\
DFO (2005).
\newblock Canada's policy for conservation of wild {Pacific} salmon.
\newblock Tech. rep., Fisheries and Oceans Canada, Vancouver, BC.

\bibitem[{Eliason \emph{et~al.}(2011)Eliason, Clark, Hague, Hanson, Gallagher,
  Jeffries, Gale, Patterson, Hinch \& Farrell}]{eliason2011}
12.\\
Eliason, E.~J., Clark, T.~D., Hague, M.~J., Hanson, L.~M., Gallagher, Z.~S.,
  Jeffries, K.~M., Gale, M.~K., Patterson, D.~A., Hinch, S.~G. \& Farrell,
  A.~P. (2011).
\newblock Differences in thermal tolerance among sockeye salmon populations.
\newblock \emph{Science}, 332, 109--112.

\bibitem[{Elmqvist \emph{et~al.}(2003)Elmqvist, Folke, Nystr{\"o}m, Peterson,
  Bengtsson, Walker \& Norberg}]{elmqvist2003}
13.\\
Elmqvist, T., Folke, C., Nystr{\"o}m, M., Peterson, G., Bengtsson, J., Walker,
  B. \& Norberg, J. (2003).
\newblock Response diversity, ecosystem change, and resilience.
\newblock \emph{Front. Ecol. Environ.}, 1, 488--494.

\bibitem[{Figge(2004)}]{figge2004}
14.\\
Figge, F. (2004).
\newblock Bio-folio: applying portfolio theory to biodiversity.
\newblock \emph{Biodivers. Conserv.}, 13, 827--849.

\bibitem[{Fraser \emph{et~al.}(2011)Fraser, Weir, Bernatchez, Hansen \&
  Taylor}]{fraser2011}
15.\\
Fraser, D.~J., Weir, L.~K., Bernatchez, L., Hansen, M.~M. \& Taylor, E.~B.
  (2011).
\newblock Extent and scale of local adaptation in salmonid fishes: review and
  meta-analysis.
\newblock \emph{Heredity}, 106, 404--420.

\bibitem[{Gustafson \emph{et~al.}(2007)Gustafson, Waples, Myers, Weitkamp,
  Bryant, Johnson \& Hard}]{gustafson2007}
16.\\
Gustafson, R.~G., Waples, R.~S., Myers, J.~M., Weitkamp, L.~A., Bryant, G.~J.,
  Johnson, O.~W. \& Hard, J.~J. (2007).
\newblock Pacific salmon extinctions: quantifying lost and remaining diversity.
\newblock \emph{Conserv. Biol.}, 21, 1009--1020.

\bibitem[{Haak \& Williams(2012)}]{haak2012}
17.\\
Haak, A.~L. \& Williams, J.~E. (2012).
\newblock Spreading the risk: native trout management in a warmer and
  less-certain future.
\newblock \emph{N. Am. J. Fish. Manage.}, 32, 387--401.

\bibitem[{Hannah \emph{et~al.}(2002)Hannah, Midgley, Lovejoy, Bond, Bush,
  Lovett, Scott \& Woodward}]{hannah2002a}
18.\\
Hannah, L., Midgley, G.~F., Lovejoy, T., Bond, W.~J., Bush, M., Lovett, J.~C.,
  Scott, D. \& Woodward, F.~I. (2002).
\newblock Conservation of biodiversity in a changing climate.
\newblock \emph{Conserv. Biol.}, 16, 264--268.

\bibitem[{Hilborn \emph{et~al.}(2003)Hilborn, Quinn, Schindler \&
  Rogers}]{hilborn2003}
19.\\
Hilborn, R.~W., Quinn, T., Schindler, D. \& Rogers, D. (2003).
\newblock Biocomplexity and fisheries sustainability.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 100, 6564--6568.

\bibitem[{Hilborn \& Walters(1992)}]{hilborn1992}
20.\\
Hilborn, R.~W. \& Walters, C. (1992).
\newblock \emph{Quantitative Fisheries Stock Assessment: Choice, Dynamics, and
  Uncertainty}.
\newblock Chapman and Hall, London.

\bibitem[{Ives \& Carpenter(2007)}]{ives2007}
21.\\
Ives, A.~R. \& Carpenter, S.~R. (2007).
\newblock Stability and diversity of ecosystems.
\newblock \emph{Science}, 317, 58--62.

\bibitem[{Johnson \& Schindler(2013)}]{johnson2013a}
22.\\
Johnson, S.~P. \& Schindler, D.~E. (2013).
\newblock Marine trophic diversity in an anadromous fish is linked to its
  life-history variation in fresh water.
\newblock \emph{Biol. Lett.}, 9, 20120824.

\bibitem[{Koellner \& Schmitz(2006)}]{koellner2006}
23.\\
Koellner, T. \& Schmitz, O.~J. (2006).
\newblock Biodiversity, ecosystem function, and investment risk.
\newblock \emph{BioScience}, 56, 977--985.

\bibitem[{Lackey(2003)}]{lackey2003}
24.\\
Lackey, R.~T. (2003).
\newblock {Pacific Northwest} salmon: Forecasting their status in 2100.
\newblock \emph{Rev. Fish. Sci.}, 11, 35--88.

\bibitem[{Margules \& Pressey(2000)}]{margules2000}
25.\\
Margules, C.~R. \& Pressey, R.~L. (2000).
\newblock Systematic conservation planning.
\newblock \emph{Nature}, 405, 243--253.

\bibitem[{Markowitz(1952)}]{markowitz1952}
26.\\
Markowitz, H. (1952).
\newblock Portfolio selection.
\newblock \emph{J. Finance}, 7, 77--91.

\bibitem[{McClure \emph{et~al.}(2008{\natexlab{a}})McClure, Carlson, Beechie,
  Pess, Jorgensen, Sogard, Sultan, Holzer, Travis, Sanderson, Power \&
  Carmichael}]{mcclure2008a}
27.\\
McClure, M.~M., Carlson, S.~M., Beechie, T.~J., Pess, G.~R., Jorgensen, J.~C.,
  Sogard, S.~M., Sultan, S.~E., Holzer, D.~M., Travis, J., Sanderson, B.~L.,
  Power, M.~E. \& Carmichael, R.~W. (2008{\natexlab{a}}).
\newblock Evolutionary consequences of habitat loss for {Pacific} anadromous
  salmonids.
\newblock \emph{Evol. Appl.}, 1, 300--318.

\bibitem[{McClure \emph{et~al.}(2008{\natexlab{b}})McClure, Utter, Baldwin,
  Carmichael, Hassemer, Howell, Spruell, Cooney, Schaller \&
  Petrosky}]{mcclure2008b}
28.\\
McClure, M.~M., Utter, F.~M., Baldwin, C., Carmichael, R.~W., Hassemer, P.~F.,
  Howell, P.~J., Spruell, P., Cooney, T.~D., Schaller, H.~A. \& Petrosky, C.~E.
  (2008{\natexlab{b}}).
\newblock Evolutionary effects of alternative artificial propagation programs:
  implications for viability of endangered anadromous salmonids.
\newblock \emph{Evol. Appl.}, 1, 356--375.

\bibitem[{McCullough(1999)}]{mccullough1999}
29.\\
McCullough, D.~A. (1999).
\newblock A review and synthesis of effects of alterations to the water
  temperature regime on freshwater life stages of salmonids, with special
  reference to {Chinook} salmon.
\newblock EPA 910-R-99-010, US Environmental Protection Agency.

\bibitem[{McElhany \emph{et~al.}(2000)McElhany, Ruckelshaus, Ford, Wainwright
  \& Bjorkstedt}]{mcelhany2000}
30.\\
McElhany, P., Ruckelshaus, M.~H., Ford, M.~J., Wainwright, T.~C. \& Bjorkstedt,
  E.~P. (2000).
\newblock {Viable Salmonid Populations} and the recovery of {Evolutionarily
  Significant Units}.
\newblock Tech. Rep. NOAA Tech. Memo. NMFS-NWFSC-42, U.S. Deptartment of
  Commerce.

\bibitem[{Moore \emph{et~al.}(2010)Moore, Mcclure, Rogers \&
  Schindler}]{moore2010}
31.\\
Moore, J.~W., Mcclure, M., Rogers, L.~A. \& Schindler, D.~E. (2010).
\newblock Synchronization and portfolio performance of threatened salmon.
\newblock \emph{Conserv. Lett.}, 3, 340--348.

\bibitem[{Mori \emph{et~al.}(2013)Mori, Furukawa \& Sasaki}]{mori2013}
32.\\
Mori, A.~S., Furukawa, T. \& Sasaki, T. (2013).
\newblock Response diversity determines the resilience of ecosystems to
  environmental change.
\newblock \emph{Biol. Rev.}, 88, 349--364.

\bibitem[{Patterson \emph{et~al.}(2007)Patterson, Skibo, Barnes, Hills \&
  Macdonald}]{patterson2007}
33.\\
Patterson, D.~A., Skibo, K.~M., Barnes, D.~P., Hills, J.~A. \& Macdonald, J.~S.
  (2007).
\newblock The influence of water temperature on time to surface for adult
  sockeye salmon carcasses and the limitations in estimating salmon carcasses
  in the {Fraser River, British Columbia}.
\newblock \emph{N. Am. J. Fish. Manage.}, 27, 878--884.

\bibitem[{Pressey \emph{et~al.}(2007)Pressey, Cabeza, Watts, Cowling \&
  Wilson}]{pressey2007}
34.\\
Pressey, R.~L., Cabeza, M., Watts, M.~E., Cowling, R.~M. \& Wilson, K.~A.
  (2007).
\newblock Conservation planning in a changing world.
\newblock \emph{Trends Ecol. Evolut.}, 22, 583--592.

\bibitem[{Quinn(2005)}]{quinn2005}
35.\\
Quinn, T.~P. (2005).
\newblock \emph{The Behaviour and Ecology of Pacific Salmon and Trout}.
\newblock American Fisheries Society, Bethesda, Maryland.

\bibitem[{{\texttt{R} Core Team}(2013)}]{r2013}
36.\\
{\texttt{R} Core Team} (2013).
\newblock \emph{\texttt{R}: {A} language and environment for statistical
  computing}.
\newblock \texttt{R} Foundation for Statistical Computing, Vienna, Austria.

\bibitem[{Rogers \& Schindler(2008)}]{rogers2008}
37.\\
Rogers, L.~A. \& Schindler, D.~E. (2008).
\newblock Asynchrony in population dynamics of sockeye salmon in southwest
  {Alaska}.
\newblock \emph{Oikos}, 117, 1578--1586.

\bibitem[{Ruckelshaus \emph{et~al.}(2002)Ruckelshaus, Levin, Johnson \&
  Kareiva}]{ruckelshaus2002}
38.\\
Ruckelshaus, M.~H., Levin, P., Johnson, J.~B. \& Kareiva, P.~M. (2002).
\newblock The {Pacific} salmon wars: what science brings to the challenge of
  recovering species.
\newblock \emph{Annu. Rev. Ecol. Syst.}, 33, 665--706.

\bibitem[{Scheuerell \emph{et~al.}(2006)Scheuerell, Hilborn, Ruckelshaus,
  Bartz, Lagueux, Haas \& Rawson}]{scheuerell2006}
39.\\
Scheuerell, M.~D., Hilborn, R., Ruckelshaus, M.~H., Bartz, K.~K., Lagueux,
  K.~M., Haas, A.~D. \& Rawson, K. (2006).
\newblock The {Shiraz} model: a tool for incorporating anthropogenic effects
  and fish--habitat relationships in conservation planning.
\newblock \emph{Can. J. Fish. Aquat. Sci.}, 63, 1596--1607.

\bibitem[{Schindler \emph{et~al.}(2008)Schindler, Augerot, Fleishman, Mantua,
  Riddell, Ruckelshaus, Seeb \& Webster}]{schindler2008}
40.\\
Schindler, D.~E., Augerot, X., Fleishman, E., Mantua, N.~J., Riddell, B.,
  Ruckelshaus, M., Seeb, J. \& Webster, M. (2008).
\newblock Climate change, ecosystem impacts, and management for {Pacific}
  salmon.
\newblock \emph{Fisheries}, 33, 502--506.

\bibitem[{Schindler \emph{et~al.}(2010)Schindler, Hilborn, Chasco, Boatright,
  Quinn, Rogers \& Webster}]{schindler2010}
41.\\
Schindler, D.~E., Hilborn, R., Chasco, B., Boatright, C.~P., Quinn, T.~P.,
  Rogers, L.~A. \& Webster, M.~S. (2010).
\newblock Population diversity and the portfolio effect in an exploited
  species.
\newblock \emph{Nature}, 465, 609--612.

\bibitem[{Schtickzelle \& Quinn(2007)}]{schtickzelle2007}
42.\\
Schtickzelle, N. \& Quinn, T.~P. (2007).
\newblock A metapopulation perspective for salmon and other anadromous fish.
\newblock \emph{Fish Fish.}, 8, 297--314.

\bibitem[{Stockwell \emph{et~al.}(2003)Stockwell, Hendry \&
  Kinnison}]{stockwell2003}
43.\\
Stockwell, C., Hendry, A. \& Kinnison, M. (2003).
\newblock Contemporary evolution meets conservation biology.
\newblock \emph{Trends. Ecol. Evol.}, 18, 94--101.

\bibitem[{Thibaut \emph{et~al.}(2012)Thibaut, Connolly \&
  Sweatman}]{thibaut2012}
44.\\
Thibaut, L., Connolly, S.~R. \& Sweatman, H. P.~A. (2012).
\newblock Diversity and stability of herbivorous fishes on coral reefs.
\newblock \emph{Ecology}, 93, 891--901.

\bibitem[{Thomas(2010)}]{thomas2010}
45.\\
Thomas, C.~D. (2010).
\newblock Climate, climate change and range boundaries.
\newblock \emph{Divers. Distrib.}, 16, 488--495.

\bibitem[{Thomas \emph{et~al.}(2004)Thomas, Cameron, Green, Bakkenes, Beaumont,
  Collingham, Erasmus, de~Siqueira, Grainger, Hannah, Hughes, Huntley, van
  Jaarsveld, Midgley, Miles, Ortega-Huerta, Townsend~Peterson, Phillips \&
  Williams}]{thomas2004}
46.\\
Thomas, C.~D., Cameron, A., Green, R.~E., Bakkenes, M., Beaumont, L.~J.,
  Collingham, Y.~C., Erasmus, B. F.~N., de~Siqueira, M.~F., Grainger, A.,
  Hannah, L., Hughes, L., Huntley, B., van Jaarsveld, A.~S., Midgley, G.~F.,
  Miles, L., Ortega-Huerta, M.~A., Townsend~Peterson, A., Phillips, O.~L. \&
  Williams, S.~E. (2004).
\newblock Extinction risk from climate change.
\newblock \emph{Nature}, 427, 145--148.

\bibitem[{Thorson \emph{et~al.}(2013)Thorson, Scheuerell, Buhle \&
  Copeland}]{thorson2013}
47.\\
Thorson, J.~T., Scheuerell, M.~D., Buhle, E.~R. \& Copeland, T. (2013).
\newblock Spatial variation buffers temporal fluctuations in early juvenile
  survival for an endangered {Pacific} salmon.
\newblock \emph{J. Anim. Ecol.}, In press. doi:10.1111/1365-2656.12117.
